### 2021-03-05 text/draft.tex
metrics per department

For each configuration, the F1-score was then computed. It is important
to note that each metric comes in three different flavors dubbed
``macro,'' ``micro,'' and ``weighted'' respectively (see Sokolova and
Lapalme 2009). In the macro flavor, the metric represents simply the
mean per class (i.e., correct or incorrect suggestion). The weighted
metric is the macro metric but each class is weighted by its true
positives. By contrast, a metric with the micro flavor is computed
globally over all true positives and false positives respectively
negatives. So the ``macro'' and ``weighted'' flavors are useful for
assessing the performance of a configuration with respect to individual
cases of assigning subject terms whereas the ``micro'' flavor is most
suitable to assess the overall performance of a configuration with
respect to assigning subject terms.

To compute the F1-score, we call
\texttt{\_Analysis.super\_make\_metrics} on
\texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output files
are saved as \texttt{/metrics/metrics\_\{marker\}} where \texttt{marker}
specifies the Annif configuration; a single file for analysis is saved
as \texttt{/analysis/metrics.json}:

@@

Note that if an item had an empty native gold standard, no score was
computed; this is the case exactly if none of the cleaned keywords had
been matched to Wikidata or YSO respectively. Configurations with a
Wikidata vocabulary had a scoring coverage of 94.38\% of the items in
the sample data set as compared to only 62.84\% for configurations with
a YSO vocabulary.

@@

>>>>

For each configuration, the F1-score was then computed. It is important
to note that each metric comes in three different flavors dubbed
``macro,'' ``micro,'' and ``weighted'' respectively (see Sokolova and
Lapalme 2009). In the macro flavor, the metric represents simply the
mean per class (i.e., correct or incorrect suggestion). The weighted
metric is the macro metric but each class is weighted by its true
positives. By contrast, a metric with the micro flavor is computed
globally over all true positives and false positives respectively
negatives. So the ``macro'' and ``weighted'' flavors are useful for
assessing the performance of a configuration with respect to individual
cases of assigning subject terms (call them ``samples'') whereas the
``micro'' flavor is most suitable to assess the overall performance of a
configuration with respect to assigning subject terms.

To compute the F1-score, we call
\texttt{\_Analysis.super\_make\_metrics} on
\texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output files
are saved as \texttt{/metrics/metrics\_\{marker\}.json} where
\texttt{marker} specifies the Annif configuration; a single file for
analysis is saved as \texttt{/analysis/metrics.json}:

@@

Note that the data foundation includes additional information, namely
the sample size and the raw values for the confusion matrix. The sample
size is a histogram of each instance in which a value in the confusion
matrix was computed, that is, each case in which either Annif or the
native gold standard assigned a subject term. Finally, note that if an
item in the Edoc sample data set had an empty native gold standard, no
score was computed; this is the case exactly if none of the cleaned
keywords had been matched to Wikidata or YSO respectively.
Configurations with a Wikidata vocabulary had a scoring coverage of
94.38\% of the items in the sample data set as compared to only 62.84\%
for configurations with a YSO vocabulary.

@@

\hypertarget{departments}{%
\paragraph{Departments}\label{departments}}

I had noted in section X as caveat that the performance of Annif might
vary according to department due to systematic biases in constructing
the Edoc sample data set. It might therefore be illuminating to assess
the performance of the various Annif configurations per department.
Since the Edoc \texttt{department} data field is mandatory, the sample
data set is partioned into blocks of departments by default. We can thus
create a data foundation for each such block by calling
\texttt{\_Analysis.super\_make\_metrics} with a departmental parameter:

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{for}\NormalTok{ dept }\KeywordTok{in}\NormalTok{ \_Data.get\_departments():}
\NormalTok{    \_Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{, deparment}\OperatorTok{=}\NormalTok{dept)}
\end{Highlighting}
\end{Shaded}

This yields 1000 files in
\texttt{/metrics/metrics\_\{department\}\_\{marker\}.json} (100
configurations \(*\) 10 departments) where \texttt{department} specifies
the department according to the Edoc convention.

\begin{itemize}
\tightlist
\item
  best config for department
\end{itemize}
